---
title: "Binom"
author: "instructor"
date: "Thursday, March 26, 2015"
output: html_document
---

using and plotting binomial distributions

```{r}
par(mfrow=c(1,2))
x=0:100
p.5=dbinom(x,size=100,prob=.5)
plot(x,p.5,type="l",main="dbinom \n p=.5")
z.5=pbinom(x,size=100,prob=.5)
plot(x,z.5,type="l",main="pbinom \n p=.5")
par(mfrow=c(1,1))
```

Lets change p to .2

```{r}
par(mfrow=c(1,2))
x=0:100
p.2=dbinom(x,size=100,prob=.2)
plot(x,p.2,type="l",main="dbinom \n p=.2")
z.2=pbinom(x,size=100,prob=.2)
plot(x,z.2,type="l",main="pbinom \n p=.2")
par(mfrow=c(1,1))
```

Lets change p to .8

```{r}
par(mfrow=c(1,2))
x=0:100
p.8=dbinom(x,size=100,prob=.8)
plot(x,p.8,type="l",main="dbinom \n p=.8")
z.8=pbinom(x,size=100,prob=.8)
plot(x,z.8,type="l",main="pbinom \n p=.8")
par(mfrow=c(1,1))
```

let's compute the mean when p=.5

```{r}
x=0:100
p.5=dbinom(x,size=100,prob=.5)
data.5=x*p.5
mean.5=sum(data.5)
mean.5
```

let's compute the mean when p=.2

```{r}
x=0:100
p.2=dbinom(x,size=100,prob=.2)
data=x*p.2
mean.2=sum(data)
mean.2
```

how about the mean when p=.8

```{r}
x=0:100
p.8=dbinom(x,size=100,prob=.8)
data.8=x*p.8
mean.8=sum(data.8)
mean.8
```
## so a random variable with a size=n and prob=p  
##has a mean of n*p  

#how about variance or standard deviation?

```{r}
x=0:100
p.5=dbinom(x,size=100,prob=.5)
data.5=x*p.5
mean.5=sum(data.5)
#now center x by subtracting mean from each element
cx.5=x-mean.5
#and now sum the squared centered x's times their probabilities
var.5=sum(cx.5^2*p.5)
sd.5=sqrt(var.5)
var.5
sd.5
```
Let' see about our other two (p=.2 and p=.8)
```{r}
x=0:100
p.2=dbinom(x,size=100,prob=.2)
data.2=x*p.2
mean.2=sum(data.2)
#now center x by subtracting mean from each element
cx.2=x-mean.2
#and now sum the squared centered x's times their probabilities
var.2=sum(cx.2^2*p.2)
sd.2=sqrt(var.2)
var.2
sd.2
```

## now for p=.8

```{r}
x=0:100
p.8=dbinom(x,size=100,prob=.8)
data.8=x*p.8
mean.8=sum(data.8)
#now center x by subtracting mean from each element
cx.8=x-mean.8
#and now sum the squared centered x's times their probabilities
var.8=sum(cx.8^2*p.8)
sd.8=sqrt(var.8)
var.8
sd.8
```
## now check against these formula's

### $mean = n*p$

### $standard deviation = \sqrt(n*p*q)$



